---
title: "Simplified Metadata"
output: 
  html_notebook: 
    highlight: tango
    theme: readable
author: Michelle M. Fink, using code from Chris Tracey & Tim Howard
---
#### Last revised: `r Sys.Date()`
#### Built on R `r getRversion()`

### 1. Required to run the code:  
```{r, message=FALSE, warning=FALSE}
library(knitr)
library(sf)
library(raster)
library(xtable)
library(tinytex)
library(stringi)
library(tables)
library(readxl)
```
(Not sure all of these ^ packages are still used with the modified code.)


+ SimplifiedMetadata_knitr.rnw
+ metadata_inputs.xlsx
+ MikTex installed, see http://miktex.org/


### 2. The spreadsheet contains metadata info that we want to knit into an abbreviated version of the MoBI metadata
Spreadsheet contains 1 tab with:  

+ Sciname  
+ CommName
+ Code1 (species code)
+ Code2 (Element ID)  
+ Grank (rounded)
+ Inputs  
+ InputSource  
+ Filename  
+ ContactName  
+ ContactOrg  
+ ContactEmail  
+ Notes (basic methods)  
+ Reviewed  
+ Final  
  
### 3. Set the variables:
(you will want to change these)
```{r}
working.dir <- "C:/Michelle/Metadata/test"
baselayers.dir <- "D:/GIS/Base/USA"
models.dir <- "M:/GIS_Projects/MOBI"
xls <- "metadata_inputs.xlsx"

ranks <- list("Critically Imperiled", "Imperiled", "Vulnerable", "Apparently Secure", "Secure")
names(ranks) <- c("G1", "G2", "G3", "G4", "G5")
states <- paste(baselayers.dir, "STATES.shp", sep = "/")
counties <- paste(baselayers.dir, "COUNTIES.shp", sep = "/")
sfstates <- st_read(states, quiet = T)
sfcounties <- st_read(counties, quiet = T)
```

### 4. Read each record in the spreadsheet and pass to knitr
```{r}
setwd(working.dir)
in.meta <- read_xlsx(xls, col_types = "text")

for (i in 1:nrow(in.meta)){
  sdm.sciname <- in.meta$SciName[i]
  sdm.comname <- in.meta$CommName[i]
  results_shape <- raster(paste(models.dir, in.meta$Filename[i], sep = "/"))
  rasext <- extent(results_shape)
  x1 <- rasext[1] - (rasext[1] * 0.01)
  x2 <- rasext[2] + (rasext[2] * 0.01)
  y1 <- rasext[3] - (rasext[3] * 0.01)
  y2 <- rasext[4] + (rasext[4] * 0.01)
  NSurl <- paste("http://explorer.natureserve.org/servlet/NatureServe?searchName=",gsub(" ", "+", sdm.sciname, fixed=TRUE), sep="")
  n <- nchar(in.meta$Filename[i])
  model_run_name <- substr(in.meta$Filename[i], 1, n-4)
  sdm.code1 <- in.meta$Code1[i]
  sdm.code2 <- in.meta$Code2[i]
  sdm.grank <- in.meta$Grank[i]
  sdm.modeler <- paste(in.meta$ContactName[i], in.meta$ContactEmail[i], in.meta$ContactOrg[i], sep = ", ")
  sdm.program <- in.meta$ContactOrg[i]
  sdm.inputs <- in.meta$Inputs[i]
  sdm.source <- in.meta$InputSource
  sdm.notes <- in.meta$Notes[i]
  sdm.review <- in.meta$Reviewed[i]
  sdm.final <- in.meta$Final[i]
  knit(paste(working.dir,"SimplifiedMetadata_knitr.rnw",sep="/"), output=paste(model_run_name, ".tex",sep=""))
  call <- paste0("pdflatex -interaction=nonstopmode ", model_run_name, ".tex")
  system(call)
}
```

**N.B.** I just barely know how to use Markdown, LaTeX is a bit beyond me. So someone please fix this up.